%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{slate-blue}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[rectangle,edge,right]{./examples/profile}
\name{Tyler}{Kuipers}
\position{Software Developer}
\address{3936 50A Street Red Deer, Alberta}

\mobile{(587) 879-4626}
\email{tkuipers123@gmail.com}
% \homepage{www.posquit0.com}
\github{tkuipers}
\linkedin{tyler-kuipers}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

% \quote{``Be the change that you want to see in the world."}
\recipient
  {AMA Insurance IT}
  {11220 109 St NW,\\Edmonton, AB\\T5G 2T6}
  % {Google Inc.\\1600 Amphitheatre Parkway\\Mountain View, CA 94043}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Agile Team Lead}
% How the letter is opened
\letteropening{Dear Hiring Manager,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Resume}

%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Tyler Kuipers~~~·~~~Cover Letter}
  {\thepage}

\makelettertitle


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%-------------------------------------------------------------------------------
\begin{cvletter}
As an enthusiastic employee of AMA, I'm excited to formally apply for the agile team lead position.  As you are aware, since joining the development team in the insurance 
division, I've quickly mastered the skills required for my position and exceeded expectations in many areas.  I have become a central source of information, and am well 
regarded in the opinions of my peers.  While I am happy with my current position, working as a team lead is more in line with my long term career goals, and I feel that
my abilities will be an immediate asset to insurance IT.

Since I have begun working at AMA as a software developer, I have taken part in many initiatives that have resulted in increased throughput and modernization of our team.
I took a lead role in our transition from SVN to Git, resulting in a more comprehensive ADO solution which is used every day by developers and others.  I took a leadership role
in many of the initiatives completed during my employment, all of which were largely succesful.  I spearheaded the unit testing initiative which is being worked into a comprehensive CI/CD pipeline that we 
will use to increase code quality in the future.  This has resulted in more stability to our system in the past, and ideally will continue to impact quality.

I have read the requirements for the team lead position thouroughly.  Although I may not be a perfect match for the position, I'm confident that the skills I have 
developed over my career, along with my passion for software development will make me an ideal fit for the role.

I appreciate your time and consideration, and look forward to discussing this at your convenience.  Please let me know if there is any other information
I can provide for you, I'd be happy to send it your way.

\end{cvletter}

\makeletterclosing



%-------------------------------------------------------------------------------
\end{document}
