\cvsection{Work Experience}

\begin{cventries}
    \cventry
        {Insurance Software Architect}
        {Alberta Motor Association}
        {Edmonton, Alberta}
        {Jan 2023 - Present}
        {
            I am working as a Software Architect on AMA's insurance systems.  Responsibilities include the following:
            \begin{itemize}
                \item Architecting and developing the cloud architecture for AMA's pay-as-you-go insurance policy, accounting for > 1400 new policies sold in the first 4 months. (AWS, Terraform, Java)
                \item Architecting and helping to implement large updates to our online payment system, helping to enable an omnichannel experience with our insurance policies.
                \item Architecting and implementing a devops tool to allow our team to
                \begin{itemize}
                    \item create new testing environments in a single command, resulting in a > 90\% reduction in time to create new environments. (AWS, Terraform, Python, Jenkins, Docker, Git)
                    \item create testing databases in a single command, resulting in drastically reduced time to diagnose production issues. (AWS, Terraform, Python)
                \end{itemize}
                \item Architecting and developing our insurance platform's RESTful APIs to enable our online auto sales platform. (OpenAPI, Gosu, Typescript, Playwright)
                \item Code reviewing and testing various patches submitted by other developers. (Git, GitHub)
                \item Improving, enforcing, and gathering feedback on coding standards across the insurance development team, resulting in increased code maintainability and reliability.
                \item Helping new developers learn how to approach legacy code throughout the insurance platform.
            \end{itemize}
        }
    \cventry
        {Software Developer}
        {Vinted}
        {Berlin, Germany}
        {Sept 2022 - Dec 2022}
        {
            I worked as a Software Developer at Vinted on their shipping platform.
            \begin{itemize}
                \item Working on high level design and implementation of a new shipping platform. (Ruby on Rails, Shopify)
                \item Writing automated tests for the new shipping platform. 
            \end{itemize}
        }
    \cventry
        {Software Developer}
        {Arterys Inc. (Aquired by Tempus Labs)}
        {Calgary, Alberta (Remote)}
        {Aug 2021 - Aug 2022}
        {
            I worked as a Software Developer for Arterys on their core platform.  Responsibilities include the following:
            \begin{itemize}
                \item Working to integrate various medical detection AI models onto our platform. (Typescript, NodeJS)
                \item Various bug fixes and feature enhancements throughout the product. (Typescript, NodeJS)
                \item Working to lower turn-around-time on results of our AI algorithms. (AWS, Chef, Redis)
                \item Code reviewing and testing various patches submitted by other developers. (Git, GitHub)
                \item Helping new developers learn how to develop our product suite. 
                \item Monitor logs and other health checking platforms for problems before clients are impacted. (Elastic, FullStory, Kibana)
            \end{itemize}
        }
    \cventry
        {Software Developer | Software Team Lead}
        {Alberta Motor Association}
        {Edmonton, Alberta}
        {Jun 2018 - Feb 2021 | Feb 2021 - Aug 2021}
        {
            I worked as a Software Developer for AMA’s Insurance Division, doing development on its core insurance product.  Responsibilities included the following:
            \begin{itemize}
                \item Leading a team of developers working on the AMA's PolicyCenter implementation. (Gosu)
                \item Leading another team contributing to an organization-wide standards initiative. 
                \item Performing scrum master responsibilities to increase team efficiency. (VSTS, Agile)
                \item Suggesting and facilitating improvement ideas brought forward by the insurance development team.
            \end{itemize}
            I also brought success to our department in the following ways:
            \begin{itemize}
                \item Led an initiative designing and programming the test framework.  It has led to a sharp reduction in bugs throughout following projects.
                \item Planned and implemented the solutions used for online payment on AMA’s website, utilizing third-party APIs and Guidewire. (Gosu, JS, OAuth)
                \item Supported my team through knowledge transfer, guidance, and open dialogue.
                \item Participated in upgrade assessment with Guidewire to determine the scope and amount of work required to upgrade AMA's instance of Guidewire to the cloud.
            \end{itemize}
        }
    \cventry
        {Software Developer}
        {Pleasant Solutions}
        {Edmonton, Alberta}
        {Jan 2018 - Jun 2018}
        {
            I worked as a full-stack developer on projects highly customized to the client’s needs.
            \begin{itemize}
                \item Created the HMI for a concrete distribution plant (C\#, TDD).
                \item Gained experience in leadership roles for small projects.
            \end{itemize}
        }
    \cventry
        {Software Engineer Associate}
        {Lockheed Martin Canada}
        {Halifax, Nova Scotia}
        {Jan 2017 - Jan 2018}
        {
            Worked as an associate software engineer developing software to be used in CMS 330.
            \begin{itemize}
                \item Contributed to an internal research project, implementing a Data Fusion module for use with Combat Management Systems. (Java, XML, SQL, Oracle ESB)
                \item Worked to develop software modules responsible for the management and status of various underwater sensors. (Java, Swing)
                % \item Worked in an Agile SCRUM environment.
                % \item Completed daily work using TDD methodologies. (JUnit, Mockito)
            \end{itemize}
        }
    \cventry
        {Software Developer/Research Assistant}
        {The King's University}
        {Edmonton, Alberta}
        {May 2014 - Sep 2016}
        {
            Worked as a full stack developer; designed and implemented an approach to dynamically reference items both spatially and temporally.
            \begin{itemize}
                \item Designed and built a website that researchers could input information into; viewers could see the data and explore it. (PHP, HTML, VanillaJS, PostgreSQL, PostGIS)
                \item Researched the method utilized and authored an undergraduate thesis documenting my contribution to the Edmonton River Atlas
                Website. (\LaTeX)
            \end{itemize}
        }

\end{cventries}
